Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-17 paper/paper.tex
#25 explain regression 1

@@

\begin{equation}
    construction_{it} = \alpha_i + \delta_t + \mathbf{1}(S_{it} > 0) + 
    \sum_{\tau = -100}^{200} \mathbf{1}(t = e^{NewState}_i + \tau)\pi_t + \varepsilon_{it}
\end{equation}

>>>>

\cite{schoenholzer2022} find a short-run cost of switching (presumably due to conflict) and a long-run benefit. They get the short-term result by looking at cities that only switched states briefly before switching back, and the long-run result by comparing that to cities that permanently stayed with their new territory. I operate in the same framework and I borrow their notation: the variable $S_{it}$ is the number of times a city switched states in period $t$. By contrast, the variable $e^{NewState}_i$ denotes the first period in which city $i$ belongs to a different state than the previous. Intuitively, in periods with $S_{it} > 0$ a city suffers short-run effects of contemporary switching, while in periods following $e^{NewState}_i$ it will be under new rule and therefore experience long-run effects of switching.

@@

\begin{equation}
    construction_{it} = \alpha_i + \delta_t + \mathbf{1}(S_{it} > 0) + 
    \sum_{\tau = -100}^{200} \mathbf{1}(t = e^{NewState}_i + \tau)\pi_t + \varepsilon_{it},
\end{equation}

where the outcome $construction_{it}$ is an indicator that equals 1 if any construction activity was recorded in city $i$ and period $t$,  the variable $S_{it}$ is the number of times a city switched states in period $t$, the variable $e^{NewState}_i$ denotes the first period in which city $i$ belongs to a different state than the previous, and $\alpha_i$ and $\delta_t$ denote city and period fixed effects.

Some comments on this. First, it may seem like a good idea to include state fixed effects. But I cannot because the hypothesised selection effect works through an improvement in state quality. State fixed effects would absorb the variation in time-invariant state quality.
